---
title: "Tinnitus_kmd"
author: "Abhilash, Kritika, Priyanka, Shivani"
date: "25/08/2019"
output: html_document
params:
  k: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = (params$k>1 && params$k<11))
```

## Motivation
* Tinnitus is a highly common health problem which severely affects people. As a Tinnitus patient, people need to fill many
questionnaires which can be tiring.

* If we know the possible sub categories of Tinnitus it would help medical practitioners to provide category specific medical assistance to the patients.

* Understanding the sub categories would also help to identify questionnaires which are only relevant to these sub categories and thus reduce the number questions patients might have to fill.

## Problem Statement
1) To identify relevant sub-categories of Tinnitus condition

2) To represent/describe the identified clusters and assign most relevant questionnaires respectively.

## Organisation

The project is organised as follows:

* Data preprocessing
* Global Clustering
* Subspace Clustering
* Evaluation

***
Let us first load all necessary libraries for this project
```{r Libraries, message=FALSE, warning=FALSE}
#If any errors are thrown while loading libraries please install the packages commented below
#install.packages("tidyverse")
#install.packages("caret")
#install.packages("rpart.plot")
#install.packages("e1071")
library(dplyr)
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms
library(r2d3)
library(sqldf)
library(caret)
library(rpart.plot)
library(e1071)
library(randomForest)
library(mlbench)
library(rJava)
library(subspace)
library(orclus)
library(diceR)
library(clValid)

```

## Data preprocessing 

Now we will step by step do the preprocessing of given data

```{r Dataframe}
df <- read_rds("190426_charite_tinnitus.rds") %>%
  arrange(.testdatum) %>%
  group_by(.jour_nr) %>%
  slice(1) %>%
  ungroup() %>%
  filter(.phase == "A") %>%
  mutate(phqk_paniksyndrom = if_else(phqk_phqk_2a +
                                       phqk_phqk_2b +
                                       phqk_phqk_2c +
                                       phqk_phqk_2d +
                                       phqk_phqk_2e == 5, 1, 0)) %>%
  select(.jour_nr,
         .age,
         acsa_acsa,
         adsl_adsl_sum,
         bi_erschoepfung, bi_magen, bi_glieder, bi_herz, bi_beschwerden,
         bsf_geh, bsf_eng, bsf_aerg, bsf_an_de, bsf_mued, bsf_tnl,
         isr_deprsyn, isr_angstsyn, isr_zwasyn, isr_somasyn, isr_essstsyn,
         isr_zusatz, isr_isr_ges,
         phqk_depressivitaet, phqk_paniksyndrom,
         psq_anford, psq_anspan, psq_freude, psq_sorgen, psq_psq_sum,
         schmerzskal_beein10, schmerzskal_haeuf10, schmerzskal_staerke10,
         ses_ses_affektiv, ses_ses_sensorisch,
         sf8_bp_sf36ks, sf8_gh_sf36ag, sf8_mcs8, sf8_mh_sf36pw, sf8_pcs8,
         sf8_pf_sf36kf, sf8_re_sf36er, sf8_rp_sf36kr, sf8_sf_sf36sf, sf8_vt_sf36vit,
         sozk_soz01_male, sozk_soz02_german, sozk_soz05_partner, sozk_soz06_married,
         sozk_soz09_abitur, sozk_soz10_keinAbschl, sozk_soz11_job, sozk_soz18_selbstst, 
         sozk_soz1920_krank, sozk_soz21_tindauer, sozk_soz2224_psycho, sozk_soz25_numdoc,
         swop_sw, swop_opt, swop_pes,
         tq_aku, tq_co, tq_em, tq_inti, tq_pb, tq_sl, tq_som, tq_tf,
         tinskal_beein10, tinskal_haeuf10, tinskal_laut10,
         starts_with("tlq"), -tlq_timestamp
  ) %>%
  drop_na()
originaldf <- read_rds("190426_charite_tinnitus.rds")
```
Now lets remove 'journ.no' as it is an identifier and will not be useful for analysis.

```{r Dataframe all features}
df_allF <- select(df,-c(.jour_nr))

#Data frame with all features "Scaled" except journ no
df_allF_scaled<-scale(df_allF)%>%data.frame()
```

We will find out the co related columns in the data and drop them

```{r Correlation}
correlated_coloumns <- data.frame(F1 = character(),F2 = character(),coef = numeric())

#cat("\ncorrelation with 90%:\n")
matriz_cor <- cor(df_allF,method = "spearman")

for (i in 1:nrow(matriz_cor)){
  correlations <-  which((abs(matriz_cor[i,]) > 0.9) & (matriz_cor[i,] != 1))
  matriz_cor[correlations,i] <- NA
  
  if(length(correlations)> 0){
    #lapply(correlations,FUN =  function(x) (cat("\t",paste(colnames(test)[i], "with",colnames(test)[x]), "\n")))
    correlated_coloumns <-  rbind(correlated_coloumns,data.frame(F1=colnames(df_allF)[i],F2=colnames(df_allF)[correlations],coef=matriz_cor[i,correlations]))
    rownames(correlated_coloumns) <- NULL
  }
}

#No correlated columns

#dropping the columns
df_noCorr <- select(df_allF,-c("sf8_mh_sf36pw","tq_tf","tq_em","tq_co"))

#Data frame with reduced features "Scaled"
df_noCorr_scaled <- scale(df_noCorr)%>%data.frame()
numClust<-params$k
```
```{r}
createDT<-function(final_labels,remove_na)
{ 
  set.seed(123)
  
  
  # labelling the records 
  df_allF_labeled<-df_allF%>%
    mutate(label = final_labels)
  df_string_labeled<-df_allF_labeled
  
  #Adding "Type" to each cluster number to make it non numeric
  df_string_labeled$label<-sub("^","Type ",df_allF_labeled$label)
  if(remove_na)
  {
    df_string_labeled <- df_string_labeled[-c(which(is.na(df_string_labeled$label))),]
  }
  
  trctrl <- trainControl(method = "boot", number = 10)
  dtree_fit <- train(label ~., data = df_string_labeled, method = "rpart",
                     parms = list(split = "information"),
                     trControl=trctrl,
                     tuneLength = 10)
  
  prp(dtree_fit$finalModel, box.palette = "Reds", tweak = 1.2)
}
```
```{r}
feature_summary_scaled<-data.frame(df_allF_scaled%>%
                                     summarise_each(mean))
feature_summary<-data.frame(df_allF%>%
                              summarise_each(mean))
options(scipen = 999)
createPlotData<-function(algo_name,clus_name,cluster_scaled,cluster)
 { cluster_plot_data<-rbind(colnames(cluster[-1]),cluster_scaled[-1],feature_summary,cluster[-1])
  rownames(cluster_plot_data)<-c("feature","scaled_cluster_feature_value","population_mean","cluster_feature_value")
  cluster_plot_data<-t(cluster_plot_data)%>%data.frame()%>%mutate(algorithm=algo_name,cluster_name=clus_name)
  return(cluster_plot_data)
}
getPlotData<-function(algo_name,final_labels,no_of_clusters)
{
  # labelling the records 
  df_allF_labeled<-df_allF%>%
  mutate(label = final_labels)
df_allF_scaled_labeled<-df_allF_scaled%>%
  mutate(label = final_labels)

# creating cluster feature vectors from obtained labels

cluster_features_scaled<-data.frame(df_allF_scaled_labeled%>%
                               group_by(label)%>%
                               summarise_each(mean))
cluster_features<-data.frame(df_allF_labeled%>%
                               group_by(label)%>%
                               summarise_each(mean))
  plotData<-list()
  for(i in seq(1:no_of_clusters))
  {
    clus_name<-paste("Type ",i)
    plotData[[i]]<-createPlotData(algo_name,clus_name,cluster_features_scaled[i,],cluster_features[i,])
  }
  return(plotData)
}

    
    


```
```{r}

  kmclust <- kmeans(df_noCorr_scaled, numClust)
  km_labels <- kmclust$cluster 
  cluster_plot_data<-getPlotData("Kmeans",km_labels,numClust)
  createDT(km_labels,0)
  
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")
``` 
```{r,echo=(numClust==3)}
  r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```
```{r}


  hkmclust <- hkmeans(df_noCorr_scaled, numClust)
  hkm_labels <- hkmclust$cluster 
  cluster_plot_data<-getPlotData("Hk-means",hkm_labels,numClust)
  createDT(hkm_labels,0)
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")
```
```{r,echo=(numClust==3)}
  r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```
```{r}

  dist_matrix<-dist(df_noCorr_scaled, method = "euclidean")
  hc <-agnes(dist_matrix, method = "ward")
  h_labels<-cutree(hc,k=numClust)
  cluster_plot_data<-getPlotData("Hierarchical",h_labels,numClust)
  createDT(h_labels,0)
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")
```
```{r,echo=(numClust==3)}
  r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```
```{r}

  set.seed(123)
  ProClus.clusters.k<- ProClus(df_noCorr_scaled,k=numClust,d=70)
  labels<-c()
  
  for ( i in 1:numClust) {
    for (j in ProClus.clusters.k[[i]]$objects) {
      labels[j] <- i
    }
  }
  cluster_plot_data<-getPlotData("Proclus",labels,numClust)
  createDT(labels,1)
  
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")
```
```{r,echo=(numClust==3)}
  r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```
```{r}
  km.pc <- prcomp(df_noCorr_scaled, center = TRUE)
  PC_num <- 18
  df_PC <- km.pc$x[,1:PC_num]
  pckmclust <- kmeans(df_PC, numClust)
  pckm_labels <- pckmclust$cluster 
  cluster_plot_data<-getPlotData("PCA K-means",pckm_labels,numClust)
  createDT(pckm_labels,0)
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")
```
```{r,echo=(numClust==3)}
  r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```
```{r}

  set.seed(123)
  library(orclus)
  orclus_res_k <- orclus(df_noCorr_scaled,k = numClust,l = 25, k0 = 20)
  ok_labels <- orclus_res_k$cluster
  cluster_plot_data<-getPlotData("Orclus",ok_labels,numClust)
  createDT(ok_labels,0)
  r2d3(data = cluster_plot_data[[1]], script = "cluster_chart.js",viewer ="internal")
  r2d3(data = cluster_plot_data[[2]], script = "cluster_chart.js",viewer ="internal")

```
```{r,echo=(numClust==3)}
 r2d3(data = cluster_plot_data[[3]], script = "cluster_chart.js",viewer ="internal")
```


