---
title: "Subspace Clustering"
author: "Priyanka"
date: "6/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(subspace)
library(ggplot2)
library(Rtsne)
library(r2d3)
#library(ChemmineR)
library(scatterplot3d)

ProClus.clusters.k2 <- ProClus(df_scaled,k=4)


#install.packages("BiocManager")
#BiocManager::install("ChemmineR")

#identify the row ID for samples in each cluster (e.g. ProClus2[[1]]$objects identifies cluster 1
#rowIDs)
cluster1<-ProClus.clusters.k2[[1]]$objects
cluster2<-ProClus.clusters.k2[[2]]$objects
cluster3<-ProClus.clusters.k2[[3]]$objects
cluster4<-ProClus.clusters.k2[[4]]$objects
```


```{r}

labels<-c()

for(i in cluster1){
  
  labels[i] <- 1
  
}
for(i in cluster2){
  
  labels[i]<- 2
  
}
for(i in cluster3){
  
  labels[i]<- 3
  
}
for(i in cluster4){
  
  labels[i]<- 4
  
}

```


```{r}

df_labeled <- df%>%
  mutate(label = labels)
df_labeled%>%head


cluster_features<-data.frame(df_labeled%>%
                               select(-.jour_nr)%>%
                               group_by(label)%>%
                               summarise_each(mean))
feature_summary<-data.frame(df%>%
                              select(-.jour_nr)%>%
                              summarise_each(mean))


#Plotting Clusters in Radial Bar Chart

cluster_features <- cluster_features[1:4,]

options(scipen = 999)

f<-function(cluster)
{ cluster_plot_data<-rbind(feature_summary,cluster[-1])
cluster_name<-paste("cluster_",cluster[1])
rownames(cluster_plot_data)<-c("general_mean",cluster_name)
cluster_plot_data<-t(cluster_plot_data)%>%data.frame()
cluster_plot_data<-mutate(cluster_plot_data,mean_difference = cluster_plot_data[,1]-cluster_plot_data[,2],feature=rownames(cluster_plot_data))
r2d3(data = cluster_plot_data, script = "cluster_chart.js",viewer ="browser")
}
apply(cluster_features,1,f)


```


ORCLUS CLUSTERING


```{r}


library(orclus)
library(ggvis)

subspace_data <- df_scaled


orclus.res <- orclus(x = subspace_data,k = 4,l = 40, k0 = 10)

```

```{r}

orcluslabels <- orclus.res$cluster
head(klabels, n = 50)

```


```{r}


df_labeled <- df%>%
  mutate(label = orcluslabels)
df_labeled%>%head

```

rouping the data based on the assigned labels and splitting into one data frame for each group.(extra step)
```{r}
df_grouped<-df_labeled%>%
  group_by(label)
df_split<-group_split(df_grouped)

```

The .journ_nr column is like an identifier for each record and is not significant for the cluster discription. So dropping that column. and then getting a summary of each cluster(group) as "cluster features"
Also calculating the general population summary for each feature as "feature summary".
```{r}
cluster_features<-data.frame(df_labeled%>%
                               select(-.jour_nr)%>%
                               group_by(label)%>%
                               summarise_each(mean))
feature_summary<-data.frame(df%>%
                               select(-.jour_nr)%>%
                               summarise_each(mean))

```


Finally creating a data frame which can be used for the visualization.
The difference between "feature_summary" and "cluster_features" will tell us how different the feature of a cluster is from the mean of the population. Which is finally plotted in the graph.
```{r echo=TRUE}
options(scipen = 999)

f<-function(cluster)
 { cluster_plot_data<-rbind(feature_summary,cluster[-1])
  cluster_name<-paste("cluster_",cluster[1])
  rownames(cluster_plot_data)<-c("general_mean",cluster_name)
  cluster_plot_data<-t(cluster_plot_data)%>%data.frame()
  cluster_plot_data<-mutate(cluster_plot_data,mean_difference =   cluster_plot_data[,1]-cluster_plot_data[,2],feature=rownames(cluster_plot_data))
  r2d3(data = cluster_plot_data, script = "cluster_chart.js",viewer ="internal")
}
apply(cluster_features,1,f)

```
